Learning a functional distance between organizations with unsupervised embeddings of scientific mobility

### 2020-07-28 paper/current/main.tex
minor edit, highlight community college, seminaries, etc.

The axes can further be visualized to examine the the relative position of organizations along the prestige axis, and along a geographic axis between California and Massachusetts that aids visualization.
Prestigious universities such as Colombia, Stanford, MIT, Harvard, and Rockefeller are positioned towards the top of the axis (Fig.~\ref{fig:semaxis}c).
Universities at the bottom of this axis tend to be regional universities with lower national profiles (yet still ranked by Times Higher Education) and with more emphasis on teaching, such as Barry University and California State University at Long Beach.
By projecting other types of organizations onto the prestige axis, SemAxis offers a new means of reasoning about the prestige of organizations for which rankings are often low-resolution or incomplete, such as regional and liberal arts universities (Fig.~\ref{fig:semaxis}d), or for which no such rankings exist, such as government organizations (Fig.~\ref{fig:semaxis}d), and research institutes (Fig.~\ref{fig:semaxis}e).

%
% Figure - SemAxis results
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=0.7\textwidth]{\figdir/SemAxis/semaxis_fig.pdf}
	\caption{
		\textbf{Embedding captures latent geography and prestige hierarchy.}
		\textbf{a.} Comparison between the ranking of organizations by their rank in the Times ranking and the embedding rank derived using SemAxis with the poles defined using the top five, and geographically-matched bottom five universities ranked by the 2018 Times Higher Education ranking of U.S. Universities .
		Un-filled points are those top and bottom five universities used to define the poles of the axis.
	  	Even when considering only a total of ten organization vectors, the estimate of the Spearman's rank correlation between the embedding and Times ranking is $\rho = 0.73$ (n = 145), and it increases if we include more top-and-bottom ranked universities (Fig.~\ref{fig:supp:semaxis_compare}).
	  	\textbf{b.} Times ranking is correlated with Leiden Ranking of U.S. universities with Spearman's $\rho = 0.87$
		\textbf{c-f.} Illustration of SemAxis projection along two axes;  \textit{latent geographical axis}, from California to Massachusetts (left to right) and the \textit{prestige axis}.
		Shown for U.S. Universities (\textbf{c}), regional and liberal arts universities (\textbf{d}), Research institutes (\textbf{e}), and Government organizations (\textbf{f}).
		Full organization names listed in Table~\ref{table:supp:orglabels}.
	}
	\label{fig:semaxis}
\end{figure}

>>>>

The axes can further be visualized to examine the the relative position of organizations along the prestige axis, and along a geographic axis between California and Massachusetts that aids visualization.
Prestigious universities such as Colombia, Stanford, MIT, Harvard, and Rockefeller are positioned towards the top of the axis (Fig.~\ref{fig:semaxis}c).
Universities at the bottom of this axis tend to be regional universities with lower national profiles (yet still ranked by Times Higher Education) and with more emphasis on teaching, such as Barry University and California State University at Long Beach.
By projecting other types of organizations onto the prestige axis, SemAxis offers a new means of reasoning about the prestige of organizations for which rankings are often low-resolution or incomplete, such as regional and liberal arts universities, seminaries, musical schools, and community colleges (Fig.~\ref{fig:semaxis}d), or for which no such rankings exist, such as government organizations (Fig.~\ref{fig:semaxis}d), and research institutes (Fig.~\ref{fig:semaxis}e).

%
% Figure - SemAxis results
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=0.7\textwidth]{\figdir/SemAxis/semaxis_fig.pdf}
	\caption{
		\textbf{Embedding captures latent geography and prestige hierarchy.}
		\textbf{a.} Comparison between the ranking of organizations by their rank in the Times ranking and the embedding rank derived using SemAxis with the poles defined using the top five, and geographically-matched bottom five universities ranked by the 2018 Times Higher Education ranking of U.S. Universities .
		Un-filled points are those top and bottom five universities used to define the poles of the axis.
	  	Even when considering only a total of ten organization vectors, the estimate of the Spearman's rank correlation between the embedding and Times ranking is $\rho = 0.73$ (n = 145), and it increases if we include more top-and-bottom ranked universities (Fig.~\ref{fig:supp:semaxis_compare}).
	  	\textbf{b.} Times ranking is correlated with Leiden Ranking of U.S. universities with Spearman's $\rho = 0.87$
		\textbf{c-f.} Illustration of SemAxis projection along two axes;  \textit{latent geographical axis}, from California to Massachusetts (left to right) and the \textit{prestige axis}.
		Shown for U.S. Universities (\textbf{c}), regional and liberal arts colleges (\textbf{d}), Research institutes (\textbf{e}), and Government organizations (\textbf{f}).
		Full organization names listed in Table~\ref{table:supp:orglabels}.
	}
	\label{fig:semaxis}
\end{figure}
